---
title: "Inequality in Incarceration Trends of the U.S."
author: "Sukyung Tae"
date: '2022-11-21'
output: html_document
---

```{r echo=FALSE, eval=TRUE, message=FALSE}
source("../source/a4-helpers.R")
source("../source/analysis.R")
```

## Abstract 


## Introduction 


## Data Summary
The total jail population in 1970 is **`r jail_population_1970`**. The total jail population in 2018 is **`r jail_population_2018`**. The state with the highest jail population was **`r state_highest_jail_population`**. Also, the state with the lowest jail population was **`r state_lowest_jail_population`**. The change of total jail population from 1970 to 2018 was **`r change_1970_to_2018`**. The black people to white people ratio of general population in the United States in 2018 was **`r black_white_ratio_general_pop_2018`** Also, that of jail population was **`r black_white_ratio_jail_pop_2018`**. Since the ratio of black people to white people is much higher in prison, there is potential of inequality in the prison system.

## Growth of the U.S. Prison Population

``` {r plot population chart, echo = FALSE}
plot(figure_1)
```


## Growth of Prison Population by State

``` {r plot population by state chart, echo = FALSE}
plot(figure_2)
```


## General Population and Prison Population by Race

``` {r plot general/jail population by race scatterplot, echo = FALSE}
plot(figure_3)
```


## Map of Jail Population by State

``` {r plot population by state map, echo = FALSE}

```
